Proposed Solution

### 2017-01-20 CAV17/secs/learner.tex
start on prob types

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking configuration errors like
missing entry errors, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second component ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (or anomalous) values 
that may violate standard practice. These anomalies can cause partial 
degradation of the system, 
such as significant reduction in performance, or even 
total failure as in Example~4 of $\S$\ref{sec-motiv}.

>>>>

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking configuration errors like
missing entry errors, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures, but can also be more insidious and slow down the system only when the load increase beyond a certain threshold.

Note that in \app, probabilistic typing is implemented as a learning module than can be easily extended to support more types.

### 2017-01-20 CAV17/secs/trans.tex
start on prob types

An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
For this reason, we introduce {\emph {probabilistic types}}.
Taking the configuration \ref{lst:mysql.cnf}, we can assume \tt{bar} is a boolean type by the grammar of MySQL,
  but the keyword {\tt bar} could either be a integer type or a Boolean type.
Now considering the rule that the keywords should have the same values ($\texttt{foo}==\texttt{bar}$), we have two potential situations.
If {\tt bar::int}, we do not learn the above rule, but in the second case where {\tt bar::bool}, the rule is valid.
To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.

Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types.
In \app, the set $\mathcal{T}$ contains strings, file paths, integers, sizes, and booleans. 
A probabilistic type is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.

@@

Note that in \app, typing is implemented as a learning module than can be easily extended to support more types.

>>>>

An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
For this reason, we introduce {\emph {probabilistic types}}.
Taking the configuration \ref{lst:mysql.cnf}, we can assume {\tt bar} is a boolean type by the grammar of MySQL,
  but the keyword {\tt bar} could either be a integer type or a Boolean type.
Now considering the rule that the keywords should have the same values ($\texttt{foo}==\texttt{bar}$), we have two potential situations.
If {\tt bar::int}, we do not learn the above rule, but in the second case where {\tt bar::bool}, the rule is valid.
To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.

Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types.
In \app, the set $\mathcal{T}$ contains strings, file paths, integers, sizes, and booleans. 
A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
A keyword may have a probabilistic type , expressed $k::\tau$, where 
The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.

@@

\begin{mathpar}
\inferrule* [Right=Bar,width=8em]
{(k,v) \in C \\ v="1"}
{k::[int}
\and
\inferrule* [lab=XX]
{uu \\ vv}{ww}
\end{mathpar}
